---
title: "create_mtc_device"
author: "System Insights"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{create_mtc_device}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Creating MTCDevice Class

You can create and MTC Device Class by specifying a Delimited MTConnect Data (DMTCD) file and a devices.XML

## DMTCD file and devices XML file - `create_mtc_device_from_dmtcd`

The usage is straightforward. The user can provide ther path to the Delimited MTConnect Data(DMTCD) file and the devices XML and the package reads the files and packages the data into an easily usable MTCDevice S4 Data Structure.

```{r}
require(mtconnectR)
file_path_dmtcd = "testdata/dataExtraction/test_dmtcd.log"
file_path_xml = "testdata/dataExtraction/test_devices.xml"
device_name = "test_device"
mtc_device = create_mtc_device_from_dmtcd(
  system.file(file_path_dmtcd, package = "mtconnectR"),
  system.file(file_path_xml, package = "mtconnectR"),
  device_name)

```

## Using the basic convenience functions

A few convenience functions are provided to help the user with the MTC Classes. They are:

### getDataItem
This function is used to get a single MTC data item from the MTC device class. If
no parameters are provided, the first data item is returned. The user can optionally enter
either a character string - in which case the data items whose paths match the character string
are returned or one or more indexes. Please note that if the pattern matches more than one
data item, a list of MTC Data Items is returned.

```{r}
# Get the first data item in the list
mtc_data_item = getDataItem(mtc_device)
print(mtc_data_item)

# Get all the data items with "Xabs" in the name
mtc_data_item = getDataItem(mtc_device, "Xabs")
print(mtc_data_item)

# Get the data item with the 5th index
mtc_data_item = getDataItem(mtc_device, 5)
print(mtc_data_item)

# Get all data items with path matching the string 'POSITION'
mtc_data_item_list = getDataItem(mtc_device, "POSITION")
print(mtc_data_item)
```

### summary

Displays a quick summary of the MTC Object with the following

* Path to each data item
* Number of Records
* Start and End times
* Type of data item (device, sample)

```{r}

print(summary(mtc_device))
print(summary(mtc_data_item))

```

### getData

If the user wants to get all the data from an MTC Object into a data.frame for further analysis,
they can use the getData method. It converts all the time series data into a data.frame object.

```{r}

# Get Data from a MTC Device Class
mtc_device_data = getData(mtc_device)
print(mtc_device_data)

# Get Data from a MTC Data item Class
mtc_data_item_data = getData(mtc_data_item)
print(mtc_data_item_data)

```

### merge

One common use case for a user doing exploratory analysis is to see how the different data items
interact with each other. The long format using `getData` method is not ideal for this. For this case,
we can use the merge function to put all the data into a single time series by merging the data items.

Also, the user can conveniently specify the pattern over which to merge or the indices to merge like
case of the `getData` method. For Example `merge(x, "abc")' will merge all the objects that have the the 
string "abc" in their name to one data frame. If no pattern is provided then all the data items are merged into one.


```{r}

# merge all the objects that have the string 'POSIT' into one data frame
print(merge(mtc_device, "POSIT"))

# merge data items with indices 3:5 into a data.frame
print(merge(mtc_device, 3:5))

# merge all the data items
merged_mtc_device = (merge(mtc_device))

# renaming column names to make it more readable
names(merged_mtc_device) = stringr::str_replace(names(merged_mtc_device), "test_device<Device>:", "")
print(merged_mtc_device)

```

