---
title: "simulate_map_gcode"
author: "System Insights"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simulate_map_gcode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

`mtconnectR` package also provides functions with further analysis capabilities. 

# Capabilities:

- G Code Parser
    - Read what each G Code block means
    - 47 different G Codes parsed
- G Code Simulator
    - Simulate Data from G Code including timestamp and values in MTConnect style (stateful, tesselated interpolation for samples)
    - Current capabilities
        - Program
        - Rapid
        - Tool Change
        - Upcoming Tool
        - Rotary Velocity/Spindle Speed
        - Path Feedrate
        - Path Position
        - Motion Linear
        - Arc Motion
- G Code Mapper
    - Given data for one instance of the part and the G Code, map the Gcode and raw data using Simulated G code values
    - Currently mapping using
        - Spindle Speed
        - Path Position Values
    - We can expand using Event (program/Tool etc) mapping, but this is not implemented yet
    
# Usage Guide

## Reading G Code data into R

```{r}
require(mtconnectR)
require(dplyr)
require(ggplot2)
gcode_file_path = "extdata/raw_gcode.NC"
gcode_parsed = parse_gcode(system.file(gcode_file_path, package = "mtconnectR"))
head(gcode_parsed)
```

## Simulating G Code data using Parse G Code.

Currently supported:

- Program
- Rapid
- Tool Change
- Upcoming Tool
- Rotary Velocity/Spindle Speed
- Path Feedrate
- Path Position
- Motion Linear
- Arc Motion

```{r}
simulated_gcode_data = na.omit(simulate_data_from_gcode(gcode_parsed, start_time = 0, data_res = 0.1, data_type = "HH"))
head(simulated_gcode_data)
mtc_device_sim = create_mtc_device_from_ts(simulated_gcode_data)
pos_data_sim = merge(mtc_device_sim, "pos")
```

## Loading MTC Data from log file

See `mtconnectR` documentation for details.
```{r}
file_path_dmtcd = "extdata/data_truncated.bz2"
file_path_xml   = "extdata/Devices.xml"
device_name = get_device_info_from_xml(
  system.file(file_path_xml, package = "mtconnectR"))$name[2]

mtc_device = create_mtc_device_from_dmtcd(system.file(file_path_dmtcd, package = "mtconnectR"),
                                          system.file( file_path_xml, package = "mtconnectR"),                                            device_name)

```


## Calculating feed rate
```{r}
calc_feed = calculated_feed_from_position(mtc_device) %>%
  mutate(value = replace(value, value < 0.1, 0)) %>% 
  clean_reduntant_rows()
mtc_device = add_data_item_to_mtc_device(mtc_device, calc_feed, data_item_type = "Sample",
                                         data_item_name = "pfr_calculated<PATH_FEEDRATE>",
                                         source_type = "calculated")
pos_data_mtc = merge(mtc_device, "path_pos") 
names(pos_data_mtc) = extract_param_from_xpath(names(pos_data_mtc), show_warnings = F)

```

## Mapping G Code to the MTC

Position and Speed(if exists) are used for mapping

````{r}
mtc_sim_mapped = map_gcode_mtc(mtc_device_sim, mtc_device, elasticity = 200)

```
## Plotting Mapped data 

```{r}
plot_twoway(mtc_sim_mapped, mtc_device_sim, mtc_device, offset = 20, total_maps = 100)

ggplot(pos_data_mtc) + geom_path(aes(x = path_pos_x, y = path_pos_y)) 

ggplot(pos_data_sim) + geom_path(aes(x = x_pos, y = y_pos)) +
  coord_cartesian(xlim = c(-2.5, 6), ylim = c(-4, 1))

ggplot(pos_data_mtc) + geom_path(aes(x = path_pos_x, y = path_pos_y)) +
  coord_cartesian(xlim = c(-2.5, 6), ylim = c(-4, 1))

```

